Feature importance analysis

### 2021-04-05 analysis/feature-importance.Rmd
wflow_publish(knitr_in("analysis/feature-importance.Rmd"), view = FALSE,     verbose = TRUE)

fi_ranked_vi <- fi_permut_vi$res %>%
  tibble::rownames_to_column("measure") %>%
  dplyr::select(-tree.number,-decoloration,-canker, -contains("ID..")) %>% 
  tidyr::pivot_longer(
    cols = !measure,
    values_to = "importance", names_to = "feature"
  ) %>%
  # mutate(wavelength = seq(420, 995, 4.75)) %>%
  dplyr::arrange(desc(importance)) %>%
  dplyr::mutate(rank = row_number()) %>%
  dplyr::select(-measure) %>%
  dplyr::mutate(feature = stringr::str_replace(feature, "bf2_", ""))
fi_ranked_vi
```

>>>>

fi_ranked_vi <- fi_permut_vi$res %>%
  tibble::rownames_to_column("measure") %>%
  dplyr::select(-contains("ID..")) %>% 
  tidyr::pivot_longer(
    cols = !measure,
    values_to = "importance", names_to = "feature"
  ) %>%
  # mutate(wavelength = seq(420, 995, 4.75)) %>%
  dplyr::arrange(desc(importance)) %>%
  dplyr::mutate(rank = row_number()) %>%
  dplyr::select(-measure) %>%
  dplyr::mutate(feature = stringr::str_replace(feature, "bf2_", ""))
fi_ranked_vi
```
